NIRCam Calibration Plan

### 2016-11-30 ms.tex
I added figures for CMD diagrams and fiber placements.
I updated the references for NGC 2506 and redid the flux_diagram to something hopefully more intuitive.

\shorttitle{NIRCam's DHS Mode}
\shortauthors{Schlawin et al.}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration for many of its science goals.

@@

\begin{table}
\centering
\caption{Cluster Parameters}\label{tab:clusterProp}
\begin{tabular}{lrrrr}
\hline \hline
Cluster   					&  E(B-V) 			& Distance Mod 	& [Fe/H] 			& Age \\
          					&     				&    (m - M)$_V$	& 	dex 			& Gyr \\
\hline \hline
NGC 2420\tablenotemark{a}	& 0.04			&  11.88			& -0.05			& 3.0 \\
NGC 2506\tablenotemark{b}	& 0.03 $\pm$0.04	&  				& 0.24 $\pm$ 0.06	& 2.3 $\pm$ 0.2 \\
NGC 6811\tablenotemark{c}	& 0.05 			& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
\hline
\end{tabular}
%\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes. The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
\tablenotetext{a}{All parameters from \citet{pancino2010chem2420}.}
\tablenotetext{b}{Parameters from \citet{lee2012openClustphot}}
\tablenotetext{c}{Parameters from \citet{molendaz2016spec6811}}
\end{table}

\section{Photometry}

@@

@@

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.7\columnwidth]{sensitivity_ladder.pdf}
\caption{Sensitivity ladder going from a narrowband, sub-array, neutral density filter observation of Sirius all the way to a wide band, full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
\end{figure}

>>>>

\shorttitle{NIRCam Flux Calibration}
\shortauthors{Schlawin et al.}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration for many of its science goals.
Many studies of dark energy make use of Type Ia Supernovae as standard candles and improvements to the absolute flux calibration are important for improving their luminosity distances.

@@

\begin{table}
\centering
\caption{Cluster Parameters}\label{tab:clusterProp}
\begin{tabular}{lrrrc}
\hline \hline
Cluster   					&  E(B-V) 			& Distance Mod 	& [Fe/H] 			& Age \\
          					&     				&    (m - M)$_V$	& 	dex 			& Gyr \\
\hline \hline
NGC 2420\tablenotemark{a}	& 0.04 $\pm$0.03	&  11.88 $\pm$ 0.27	& -0.05 $\pm$ 0.03	& 3 $\pm$ 1 \\
NGC 2506\tablenotemark{b}	& 0.058 $\pm$ 0.001	&  12.75 $\pm$ 0.10 	& -0.32 $\pm$ 0.03	& 1.85 $\pm$ 0.05 \\
NGC 6811\tablenotemark{c}	& 0.05 $\pm$0.02	& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
\hline
\end{tabular}
%\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes. The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
\tablenotetext{a}{All parameters from \citet{pancino2010chem2420}.}
\tablenotetext{b}{Parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
\tablenotetext{c}{Parameters from \citet{molendaz2016spec6811}}
\end{table}

\section{Pan-Starrs Photometry}

@@

\begin{figure*}[!t]
\centering
\subfloat[NGC 2420]{
	\includegraphics[width=0.5\textwidth]{sources_ngc2420.png}
	\label{fig:cmdNGC6811}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.5\textwidth]{sources_ngc2506.png}
	\label{fig:cmdNGC2506}
	}
\\
\subfloat[NGC 6811]{
	\includegraphics[width=0.5\textwidth]{sources_ngc6811.png}
	\label{fig:cmdNGC6811}
	}
	\caption{Color-magnitudes of the 3 clusters.}
	\label{fig:cmdPS}
\end{figure*}

@@

\section{NIRCam Footprint}
\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{nircam_fov_fibers.pdf}
\caption{NGC 2420 fibers on the first pass with the FOV of both the A and B modules of NIRCam.
Only 10 stars fit within NIRCam's FOV.}\label{fig:NCFOV}
\end{figure}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
\end{figure}
